---
title: "RMarkdown Report_HW_2"
author: "Vidhi Khare"
date: "7 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Question:
Compare these neighbouring postcodes for each of the five previous years (in our data, a year begins on 1 July): 5160, 5161. Use a selection of tables, plots and text to describe the trends in 'PROPERTY DAMAGE AND ENVIRONMENTAL' over this time period. What do you notice about these trends?

-**Aim:**

*There are 1145 suburbs in Adelaide as per the combined Excel sheet data. Our Aim is to investigate and find out the trend of crime/offence according to the different Offence level Descriptions and Offence count as per the reportes dates in various Adelaide suburbs.
This will help the Investigation Agencies to take actions as per the severity of the different types of offence happening in the suburbs.
 Example: We are comparing the neighbouring postcodes for each of the five previous years. By using a selection of tables, plots and text, we will descrie the trends in 
 'Property Damage and Environmental' which is one of the Offences, over this time period.*




```{r}
df <- data.frame(x = 1:10,
           y = 11:20)
library(knitr)
kable(df)
```
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```
library(data)

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
